---
title: "Analysis Lasso-Re (Connectom)"
date: "`r Sys.Date()`"
author: "Cher Yang"
output:
  html_document:
    code_folding: hide
    theme: yeti
    toc: yes
    toc_depth: 3
    toc_float: yes
  pdf_document:
    toc: yes
    toc_depth: '3'
  word_document:
    toc: yes
    toc_depth: '3'
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, cache = TRUE, warning = FALSE, message = FALSE)
library(tidyverse)
library(dplyr)
library(magrittr)
library(ggplot2)
library(ggthemes)
library(ppcor)
library(reshape2)
#library(gglasso)
library(glmnet)
library(ggsci)
library(viridis)
library(ggExtra)
library(kableExtra)
library(xtable)
library(ggrepel)
library(scales)
library(car)
library(pROC)
library(patchwork)      # Multi-plot alignment
library(brainconn)
library(igraph)
library(network)
library(brainconn)
library(brainGraph)
library(RColorBrewer)
library(networkD3)
library(ggpubr)
library(DescTools)
library(plotly)
#library(data.table)
library(rsample)   
library(purrr)
library(dplyr)
library(ggplot2)
library(scales)
library(mlbench)
library(kernlab)
library(sessioninfo)

library(circlize)

rm(list=ls())
```

**Analysis parameters:**

*iGraph Parameters*

-   connectom betas: refit full dataset using nested best lambda
-   connection counts (duplicates): YES

# Load Data 

Load intermediate data after running `worksapce_ml.RData`

```{r}
load(file = "../data/__cache__/worksapce_ml.RData")

USE_NESTED <- TRUE 
SAVE_PLOT <- FALSE
```


# Brain Network Analysis (Power)

## A Matrix

To calculate the averaged corr matrix A

1)  find the Fisher's Z values of the corresponding Pearson correlation
    coefficients
2)  Average them
3)  Find the reverse Fisher's Z transform of that average value.

```{r}
C.z <- FisherZ(C)
C.zmean <- matrix(colMeans(C.z), nrow=264, ncol = 264)
A <- FisherZInv(C.zmean)
A.vec <- as.vector(A)
```

## W Matrix

Calculate W from betas and A Matrix

```{r}
connectom2matrix <- function(connectome, w) {
  empty_mat <- matrix(0, 264, 264, dimnames = list(paste0("X", 1:264), paste0("X", 1:264))) 
  empty_mat[connectome$index] <- connectome$W
  return(empty_mat)
}

# convert a 264*264 matrix back to connectom df
matrix2connectom <- function(mat, connectome, col_name) {
  connectome$temp = mat[connectome$index]
  connectome <- rename(connectome, !!col_name := temp)
  return(connectome)
}

# make the matrix symmetric
make_symmetric <- function(m) {
  # lower.tri is 0.0
  m[lower.tri(m)] <- t(m)[lower.tri(m)]
  return(m)
}

power_atals <- power2011 %>% 
  rename(ROI.Name = ROI, x.mni=X, y.mni=Y, z.mni=Z, network=NetworkName) %>% 
  mutate(ROI.Name=as.integer(ROI.Name), index = as.integer(ROI.Name),
         x.mni=as.integer(x.mni), y.mni=as.integer(y.mni), z.mni=as.numeric(z.mni)) %>%
  dplyr::select(ROI.Name, x.mni, y.mni, z.mni, network, index)

check_atlas(power_atals)
```



```{r}


if(USE_NESTED) {
  connectome_data <- connectome_nested
} else {
  connectome_data <- connectome
}

Wconnectome <- connectome_data %>%
  mutate(A = A.vec[connectome_data$index], W = A*Beta)
  #separate(connection, c("connection1", "connection2"))%>%
  #separate(network, sep = "-", c("network1", "network2"), remove = F) %>%
  #filter(str_detect(network, pattern = "-1-")) %>%
         #network1 = ifelse(str_detect(network, pattern = "-1-"), -1, network1)) %>%
  #mutate(connection_type = ifelse(network1==network2, "Within", "Between"))

W_mat <- matrix(0, ncol = 264, nrow = 264)
W_mat[Wconnectome$index] <- Wconnectome$W
W_mat <- make_symmetric(W_mat) #CHECKED correct W_mat


rownames(W_mat) = power_atals$network
colnames(W_mat) = power_atals$network
```

## Declarative Network 

```{r}
power_color = power2011 %>% 
  filter(NetworkName!="Sensory/somatomotor Mouth") %>%
  select(NetworkName, Color) %>% 
  distinct() 

colors <- c(Uncertain = power_color$Color[9], #power_color$Color[1], 
            `Sensory/somatomotor Hand` = power_color$Color[6], #power_color$Color[2], 
            `Cingulo-opercular Task Control` = power_color$Color[3],
            Auditory = power_color$Color[4],
            `Default mode` = power_color$Color[5], 
            `Memory retrieval?` = power_color$Color[2], #power_color$Color[6],
            `Ventral attention` = power_color$Color[7], 
            Visual = power_color$Color[8],
            `Fronto-parietal Task Control` = power_color$Color[1], #power_color$Color[9],
            Salience = power_color$Color[10],
            Subcortical = power_color$Color[11], 
            Cerebellar = power_color$Color[12], 
            `Dorsal attention` = power_color$Color[13])

colors <- c(Uncertain = power_color$Color[1], 
            `Sensory/somatomotor Hand` = power_color$Color[2],  
            `Cingulo-opercular Task Control` = power_color$Color[3],
            Auditory = power_color$Color[4],
            `Default mode` = power_color$Color[5], 
            `Memory retrieval?` = power_color$Color[6], 
            `Ventral attention` = power_color$Color[7], 
            Visual = power_color$Color[8],
            `Fronto-parietal Task Control` = power_color$Color[9], 
            Salience = power_color$Color[10],
            Subcortical = power_color$Color[11], 
            Cerebellar = power_color$Color[12], 
            `Dorsal attention` = power_color$Color[13])
```

```{r width=15}
if (SAVE_PLOT) {
  png(filename = "analysis_lasso_re_3connectom/figure-html/network_figure1.png",  bg = "transparent", 
    width = 800 , height = 800, 
    units = "px", res = 150)
  
  circos.clear()
  chordDiagram(W_mat, directional = FALSE, transparency = 0.5, self.link = 1, 
             symmetric = TRUE, scale = TRUE, reduce = FALSE, 
             annotationTrackHeight = mm_h(c(15, 1)),
             annotationTrack = c("grid"),
             grid.col = colors, col = ifelse(W_mat>0, "tomato", "#00000000")) 
  title("Predictive Group: Declarative (W > 0)", outer = F, cex.main = 1.5)
} else {
  circos.clear()
  chordDiagram(W_mat, directional = FALSE, transparency = 0.5, self.link = 1, 
             symmetric = TRUE, scale = TRUE, reduce = FALSE, 
             #annotationTrackHeight = mm_h(c(15, 1)),
             #annotationTrack = c("grid"),
             grid.col = colors, col = ifelse(W_mat>0, "tomato", "#00000000")) 
  title("Predictive Group: Declarative (W > 0)", outer = F, cex.main = 1.5)
  
  }


```


## Procedural Network 

```{r width=15}
if (SAVE_PLOT) {
  png(filename = "analysis_lasso_re_3connectom/figure-html/network_figure2.png",  bg = "transparent", 
    width =800 , height = 800, 
    units = "px", res = 150)

  circos.clear()
  chordDiagram(W_mat, directional = FALSE, transparency = 0.5, self.link = 1, 
               symmetric = TRUE, scale = TRUE, reduce = FALSE, 
               annotationTrackHeight = mm_h(c(15, 1)),
               annotationTrack = c("grid"),
               grid.col = colors, col = ifelse(W_mat<0, "steelblue", "#00000000"))
  title("Predictive Group: Procedural (W < 0)", outer = F, cex.main = 1.5) 
  } else {
  circos.clear()
  chordDiagram(W_mat, directional = FALSE, transparency = 0.5, self.link = 1, 
               symmetric = TRUE, scale = TRUE, reduce = FALSE, 
               #annotationTrackHeight = mm_h(c(15, 1)),
               #annotationTrack = c("grid"),
               grid.col = colors, col = ifelse(W_mat<0, "steelblue", "#00000000"))
  title("Predictive Group: Procedural (W < 0)", outer = F, cex.main = 1.5)
}
```



```{r}
circos.clear()
chordDiagram(W_mat, directional = FALSE, transparency = 0.5, self.link = 1, 
             symmetric = TRUE, scale = TRUE, reduce = FALSE, 
             order = unique(power2011$NetworkName),  
             preAllocateTracks = 1,
             annotationTrackHeight = mm_h(c(10, 10)),
             annotationTrack = c("grid"),
             grid.col = colors, col = ifelse(W_mat>0, "tomato", "steelblue"))
title("Declarative + Procedural Network",  cex.main = 2)
circos.trackPlotRegion(track.index = 1, panel.fun = function(x, y) {
  xlim = get.cell.meta.data("xlim")
  ylim = get.cell.meta.data("ylim")
  sector.name = get.cell.meta.data("sector.index")
  circos.text(mean(xlim), ylim[1] + .1, sector.name, facing = "clockwise", niceFacing = TRUE, adj = c(0, 0.5))
  circos.axis(h = "top", labels.cex = 0.5, major.tick.percentage = 0.2, sector.index = sector.name, track.index = 2)
}, bg.border = NA)
```

```{r eval=FALSE, include=FALSE}

# double check

circos.clear()
chordDiagram(W_mat, directional = FALSE, transparency = 0.5, self.link = 2, 
             symmetric = TRUE, scale = F, reduce = F, 
             preAllocateTracks = 1,
             annotationTrackHeight = mm_h(c(10, 5)),
             annotationTrack = c("grid"),
             grid.col = colors, col = ifelse(W_mat<0, "steelblue", "#00000000"))
#title("Declarative Network",  cex.main = 2)
circos.trackPlotRegion(track.index = 1, panel.fun = function(x, y) {
  xlim = get.cell.meta.data("xlim")
  ylim = get.cell.meta.data("ylim")
  sector.name = get.cell.meta.data("sector.index")
  circos.text(mean(xlim), ylim[1] + .1, sector.name, facing = "clockwise", niceFacing = TRUE, adj = c(0, 0.5))
  circos.axis(h = "top", labels.cex = 0.5, major.tick.percentage = 0.2, sector.index = sector.name, track.index = 2)
}, bg.border = NA)
```



## Network and node desciptives

Next, we will look at Graph properties of two networks

###Graph Density

The proportion of present edges from all possible edges in the network.

```{r}
# select cols
roi_links <- Wconnectome %>% dplyr::select(connection1, connection2, W, connection_type, network, network_names)
# rename cols
colnames(roi_links) <- c("from", "to", "weight", "connection_type", "network", "network_names")

roi_nodes <- power2011 %>% rename(id = ROI) %>%
  mutate(NetworkName=factor(NetworkName), 
         Color=factor(Color))
levels(roi_nodes$Color) <- sample(colors(T), 14) 

# create a graph
net <- graph_from_data_frame(d=roi_links, vertices=roi_nodes, directed=F) 
#g <- graph_from_adjacency_matrix(W_mat,, mode = "upper")

net.d <- net - E(net)[E(net)$weight<0]
net.p <- net - E(net)[E(net)$weight>0]

df.density <- data.frame("edge_density"=c(edge_density(net.d, loops=F), 
                            edge_density(net.p, loops=F),
                            edge_density(net, loops=F)), 
           "network" = factor(c("Declarative", "Procedural", "Full"), levels = c("Declarative", "Procedural", "Full")))
```

```{r}
df.density %>% ggbarplot(x="network", y="edge_density", color = "white", fill=c("tomato", "steelblue", "gray"), width = 0.5, label = T, lab.nb.digits = 5) +
  theme_pander() + 
  ggtitle("Degree Edge Density")
```

### Graph: Diameter

A network diameter is the longest geodesic distance (length of the
shortest path between two nodes) in the network. In igraph, diameter()
returns the distance, while get_diameter() returns the nodes along the
first found path of that distance.

```{r}
# make negative weights to positive
net.p.abs <- net.p
E(net.p.abs)$weight <- E(net.p.abs)$weight * (-1)

# make negative weights to positive
net.abs <- net
E(net.abs)$weight[E(net.abs)$weight<0] <- E(net.abs)$weight[E(net.abs)$weight<0] * (-1)


df.diameter <- data.frame("diameter"=c(diameter(net.d, directed=F), 
                        diameter(net.p.abs, directed=F),
                        diameter(net.abs, directed=T)), 
           "network" = factor(c("Declarative", "Procedural", "Full"), levels = c("Declarative", "Procedural", "Full")))
```

```{r}
df.diameter %>% ggbarplot(x="network", y="diameter", color = "white", fill=c("tomato", "steelblue", "gray"), width = 0.5, label = T, lab.nb.digits = 5) +
  theme_pander() + 
  ggtitle("Network Diameter")
```

### Graph: Centrality Degree
 

Centrality functions (vertex level) and centralization functions (graph
level). The centralization functions return res - vertex centrality,
centralization, and theoretical_max - maximum centralization score for a
graph of that size. The centrality function can run on a subset of nodes
(set with the vids parameter). This is helpful for large graphs where
calculating all centralities may be a resource-intensive and
time-consuming task.

Centrality is a general term that relates to measures of a node's
position in the network. There are many such centrality measures, and it
can be a daunting task to wade through all of the different ways to
measure a node's importance in the network. Here, we will introduce just
a few examples.

```{r}
df.centrality <- data.frame("centr_degree"=c(centr_degree(net.d, normalized=T)$centralization, 
                        centr_degree(net.p, normalized=T)$centralization,
                        centr_degree(net, normalized=T)$centralization), 
           "network" = factor(c("Declarative", "Procedural", "Full"), levels = c("Declarative", "Procedural", "Full")))
```

```{r}
df.centrality %>% ggbarplot(x="network", y="centr_degree", color = "white", fill=c("tomato", "steelblue", "gray"), width = 0.5, label = T, lab.nb.digits = 5) +
  theme_pander() + 
  ggtitle("Network Degree Centrality ")
```


### Graph: Betweeness (Closeness)


Let's now do the same for betweenness centrality, which is defined as
the number of geodesic paths (shortest paths) that go through a given
node. Nodes with high betweenness might be influential in a network if,
for example, they capture the most amount of information flowing through
the network because the information tends to flow through them. Here, we
use the normalized version of betweenness.

Closeness (centrality based on distance to others in the graph) Inverse
of the node's average geodesic distance to others in the network.

```{r}
df.sloseness <- data.frame("centr_clo"=c(centr_clo(net.d)$centralization, 
                        centr_clo(net.p)$centralization,
                        centr_clo(net)$centralization), 
           "network" = factor(c("Declarative", "Procedural", "Full"), levels = c("Declarative", "Procedural", "Full")))
```

```{r}
df.sloseness %>% ggbarplot(x="network", y="centr_clo", color = "white", fill=c("tomato", "steelblue", "gray"), width = 0.5, label = T, lab.nb.digits = 5) +
  theme_pander() + 
  ggtitle("Network Closeness")
```

### Graph: Distances

```{r}
df.distance <- data.frame("mean_distance"=c(mean_distance(net.d, directed=F), 
                        mean_distance(net.p, directed=F),
                        mean_distance(net, directed=F)), 
           "network" = factor(c("Declarative", "Procedural", "Full"), levels = c("Declarative", "Procedural", "Full")))
```

```{r}
df.distance %>% ggbarplot(x="network", y="mean_distance", color = "white", fill=c("tomato", "steelblue", "gray"), width = 0.5, label = T, lab.nb.digits = 5) +
  theme_pander() + 
  ggtitle("Network Closeness")
```

### Graph: Assortativity

```{r}
df.assortativity<- data.frame("assortativity_degree"=c(assortativity_degree(net.d, directed=F), 
                        assortativity_degree(net.p, directed=F),
                        assortativity_degree(net, directed=F)), 
           "network" = factor(c("Declarative", "Procedural", "Full"), levels = c("Declarative", "Procedural", "Full"))) 
```

```{r}
df.assortativity %>% ggbarplot(x="network", y="assortativity_degree", color = "white", fill=c("tomato", "steelblue", "gray"), width = 0.5, label = T, lab.nb.digits = 5) +
  theme_pander() + 
  ggtitle("Network Assortativity Degree")
```
> Combined Table

```{r}
options(scipen=999)
df.density %>% 
  select(network, edge_density) %>%
  left_join(df.diameter) %>%
  left_join(df.centrality) %>%
  left_join(df.sloseness) %>%
  left_join(df.distance) %>%
  left_join(df.assortativity) %>%
  rename("centrality_degree"=centr_degree, 
         "centrality_closeness"=centr_clo) %>%
  kable(format.args = list(scientific = TRUE, big.mark = ",", digit=3))

```



### Graph:  Similarity Measurement

 
### W values in Brain Connectom

```{r}
#colors <- factor(power_atals$network)
#levels(colors) <- colors14
#power_atals$colors <- as.character(temp)
check_atlas(power_atals)
x1 <- W_mat
x1[x1<0] <- 0


p1 <- brainconn(atlas=power_atals, conmat=x1, node.color = power2011$Color, view = "top",
          node.size = igraph::degree(net.d)*2.5, all.nodes = TRUE, 
          edge.color = "tomato",  edge.color.weighted = FALSE, scale.edge.width = c(1,3), edge.alpha = 0.6,
          label.edge.weight = F,  show.legend = F,
          background.alpha = .3) #+ ggtitle("Strategy Predictability: W")
p2 <- brainconn(atlas=power_atals, conmat=x1, node.color = power2011$Color, view = "left",
          node.size = igraph::degree(net.d)*2.5, all.nodes = TRUE, 
          edge.color = "tomato",  edge.color.weighted = FALSE, scale.edge.width = c(1,3), edge.alpha = 0.6,
          label.edge.weight = F,  show.legend = F,
          background.alpha = .3) #+ ggtitle("Strategy Predictability: W")
p3 <- brainconn(atlas=power_atals, conmat=x1, node.color = power2011$Color, view = "back",
          node.size = igraph::degree(net.d)*2.5, all.nodes = TRUE, 
          edge.color = "tomato",  edge.color.weighted = FALSE, scale.edge.width = c(1,3), edge.alpha = 0.6,
          label.edge.weight = F,  show.legend = F,
          background.alpha = .3) #+ ggtitle("Strategy Predictability: W")

x2 <- W_mat
x2[x2>0] <- 0

p4 <- brainconn(atlas=power_atals, conmat=x2*-10, node.color = power2011$Color, view = "top",
          node.size = igraph::degree(net.p)*2.5, all.nodes = TRUE, 
          edge.color = "steelblue",  edge.color.weighted = FALSE, 
          scale.edge.width = c(1,3), edge.alpha = 0.6,
          label.edge.weight = F,  show.legend = F,
          background.alpha = .3)  



p5 <- brainconn(atlas=power_atals, conmat=x2*-10, node.color = power2011$Color, view = "left",
          node.size = igraph::degree(net.p)*2.5, all.nodes = TRUE, 
          edge.color = "steelblue",  edge.color.weighted = FALSE, 
          scale.edge.width = c(1,3), edge.alpha = 0.6,
          label.edge.weight = F,  show.legend = F,
          background.alpha = .3) 

p6 <- brainconn(atlas=power_atals, conmat=x2*-10, node.color = power2011$Color, view = "back",
          node.size = igraph::degree(net.p)*2.5, all.nodes = TRUE, 
          edge.color = "steelblue",  edge.color.weighted = FALSE, 
          scale.edge.width = c(1,3), edge.alpha = 0.6,
          label.edge.weight = F,  show.legend = F,
          background.alpha = .3) 
```

```{r}
if (SAVE_PLOT) {
  png(filename = "analysis_lasso_re_3connectom/figure-html/network_figure4.png",  bg = "transparent", 
      width =500, height = 500, units = "px", res = 150) }
p1
```

```{r}
if (SAVE_PLOT) {
  png(filename = "analysis_lasso_re_3connectom/figure-html/network_figure5.png",  bg = "transparent", 
      width =500, height = 500, units = "px", res = 150)} 
p2
```

```{r}
if (SAVE_PLOT) {
  png(filename = "analysis_lasso_re_3connectom/figure-html/network_figure6.png",  bg = "transparent", 
      width =500, height = 500, units = "px", res = 150)}
p3
```

```{r}
if (SAVE_PLOT) {
  png(filename = "analysis_lasso_re_3connectom/figure-html/network_figure7.png", 
      bg = "transparent", width =500, height = 500, units = "px", res = 150)}
p4
```

```{r}
if (SAVE_PLOT) {
  png(filename = "analysis_lasso_re_3connectom/figure-html/network_figure8.png",  bg = "transparent", 
      width =500, height = 500, units = "px", res = 150)}

p5
```

```{r}
if (SAVE_PLOT) {png(filename = "analysis_lasso_re_3connectom/figure-html/network_figure9.png",  bg = "transparent", 
                    width =500, height = 500, units = "px", res = 150)}

p6
```

```{r eval=FALSE, include=FALSE}
x1[,] <-1
brainconn(atlas=power_atals, conmat=x1, node.color = power2011$Color, view = "top",
          node.size = 2, all.nodes = TRUE, 
          edge.color = "tomato",  edge.color.weighted = FALSE, scale.edge.width = c(1,3), edge.alpha = 0.6,
          
          background.alpha = .3)

# Add a legend
legend(1, 95, legend=power_atals$network, 
       col=power2011$Color, lty=1:2, cex=0.8)
```

### Distribution of connections 

Look at the distribution of network in two groups

```{r}

DUPLICATE <- TRUE

c1 <- Wconnectome %>% filter(W>0) %>% mutate(roi = as.integer(connection1)) %>% dplyr::select(roi) %>%  unlist()
c2 <- Wconnectome %>% filter(W>0) %>% mutate(roi = as.integer(connection2)) %>% dplyr::select(roi) %>%  unlist()


c3 <- Wconnectome %>% filter(W<0) %>% mutate(roi = as.integer(connection1)) %>% dplyr::select(roi) %>%  unlist()
c4 <- Wconnectome %>% filter(W<0) %>% mutate(roi = as.integer(connection2)) %>% dplyr::select(roi) %>%  unlist()


if (DUPLICATE) {
  c12 <- c(c1, c2)
  c34 <- c(c3, c4)
} else {
  c12 <- unique(c(c1, c2))
  c34 <- unique(c(c3, c4))
}

df.c1 <- power2011[c12,] %>%
  mutate(NetworkName = factor(NetworkName)) %>%
  count(NetworkName, name = "count", .drop = F)%>%
  right_join(power2011 %>% dplyr::select(NetworkName, Color) %>% distinct(), on="NetworkName") %>%
  mutate(count=as.integer(ifelse(is.na(count), 0, count))) %>%
  arrange(NetworkName)

p7 <- power_color %>% 
  left_join(df.c1) %>%
  ggplot(aes(x=count, y=NetworkName)) +
  geom_col(fill = power_color$Color) +
  scale_fill_manual(guide = guide_legend(reverse = F), 
                    values = df.c1$Color, 
                    labels =  df.c1$Color) +
  scale_x_reverse() +
  theme_pander() +
  ggtitle("Distribution of connections", subtitle = "Declarative Network") +
  theme(legend.position = "right", 
        axis.text.y = element_blank(), 
        axis.title.y = element_blank(),
        plot.title = element_text(size = 20),
        axis.text = element_text(size = 20),
        legend.title = element_text(size = 20),
        legend.text = element_text(size = 20))

p7
```

```{r}

# count number of networks included in
df.c2 <- power2011[c34,] %>%
  mutate(NetworkName = factor(NetworkName)) %>%
  count(NetworkName, name = "count", .drop = F) %>%
  right_join(power2011 %>% dplyr::select(NetworkName, Color) %>% distinct(), on="NetworkName") %>%
  mutate(count=ifelse(is.na(count), 0, count)) %>%
  arrange(NetworkName) 



p8 <- power_color %>% 
  left_join(df.c2) %>%
  ggplot(aes(y = count, x=NetworkName)) +
  geom_col(fill = power_color$Color) +
  coord_flip() +
  scale_fill_manual(guide = guide_legend(reverse = F), values = power_color$Color) +
  theme_pander() +
  ggtitle("Distribution of connections", subtitle = "Procedural Network") +
  theme(legend.position = "right", 
        axis.text.y = element_blank(), 
        axis.title.y = element_blank(),
        plot.title = element_text(size = 20),
        axis.text = element_text(size = 20),
        legend.title = element_text(size = 20),
        legend.text = element_text(size = 20))



p8

```

```{r}
if (SAVE_PLOT) {
  png(filename ="analysis_lasso_re_3connectom/figure-html/network_figure10.png",  bg = "transparent", 
    width = 2000, height = 2000, 
    units = "px", res = 300)}

ggbarplot(df.c2 , x="NetworkName", y="count", fill = "NetworkName", color="white",
          palette = df.c2$Color, #order = "count",    
          legend = "right",
          rotate = TRUE, ggtheme = theme_pander(),
          title = "Distribution of connections") +
labs(fill = "Network Name")

# ggbarplot(df.c2 , x="NetworkName", y="count", fill = "NetworkName", color="white",
#           palette = df.c2$Color, #order = "count",    
#           
#           rotate = TRUE, ggtheme = theme_pander(),
#           title = "Distribution of connections") +
#   scale_y_continuous(limits = c(0,15), breaks=c(0,5, 10, 15)) +
#   scale_fill_discrete(breaks=rev(df.c2$NetworkName), ) +
#   scale_fill_discrete(guide = guide_legend(reverse=TRUE)) +
#   theme(legend.position = "right",
#         axis.text.y = element_blank(),
#         axis.title.y = element_blank(),
#         plot.title = element_text(size = 20),
#         axis.text = element_text(size = 20),
#         legend.title = element_text(size = 20),
#         legend.text = element_text(size = 20))

```

```{r fig.height=5, fig.width=18}
if (SAVE_PLOT) {
  png(filename = "analysis_lasso_re_3connectom/figure-html/network_figure10.png",  bg = "transparent", 
    width =3000, height = 1000, 
    units = "px", res = 150)}

ggarrange(p7, NULL, NULL, NULL, p8, 
          #labels = c("A", "B", "C"),
          ncol = 5, nrow = 1, align = "h", 
          common.legend = TRUE, legend = "bottom", widths = c(1,.8,.8,1))

```


Chi-sq Test

```{r}
chisq.test(df.c1$count, df.c2$count, simulate.p.value = T, p = noi_stats$N)
```

---

